MSHS COVID-19 Vaccinations

### 2021-09-09 Empl_Arrival_Tracking.Rmd
Update daily and ad hoc vaccine reporting and export scripts to account for third doses.
Add scroll boxes to daily employee vaccination report.

empl_arr_df <- employee_arr %>%
  filter(PatientType == "Employee" &
           ApptDate >= empl_arr_start_date) %>%
  mutate(PatientType = NULL)

@@

  kable(data, format = "html", escape = FALSE,
        align = "c", digits = 0,
        caption = paste("Dose", dose, "Employee Vaccine Arrivals")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           ncol(data) - 1,
                           ncol(data)),
                border_right = "thin solid lightgray") %>%
    column_spec(column = ncol(data),
                bold = TRUE,
                italic = TRUE) %>%
    add_header_above(c(" " = 1, "Date" = ncol(data) - 1),
                     background = c("",
                                    sinai_colors[1]),
                     line = FALSE,
                     color = "white") %>%
    row_spec(row = nrow(data),
             bold = TRUE,
             italic = TRUE,
             hline_after = TRUE)
}
```

>>>>

empl_arr_df <- arr_pt_type_summary %>%
  filter(PatientType == "Employee" &
           ApptDate >= empl_arr_start_date) %>%
  mutate(PatientType = NULL)

@@

  kable(data, format = "html", escape = FALSE,
        align = "c", digits = 0,
        caption = paste("Dose", dose, "Employee Vaccine Arrivals")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           ncol(data) - 1,
                           ncol(data)),
                border_right = "thin solid lightgray") %>%
    column_spec(column = ncol(data),
                bold = TRUE,
                italic = TRUE) %>%
    add_header_above(c(" " = 1, "Date" = ncol(data) - 1),
                     background = c("",
                                    sinai_colors[1]),
                     line = FALSE,
                     color = "white") %>%
    row_spec(row = nrow(data),
             bold = TRUE,
             italic = TRUE,
             hline_after = TRUE) %>%
    scroll_box(width = "800px")
}
```
